% Start a document with the here given default font size and paper size.
\documentclass[11pt]{article}

% Set the page margins.
\usepackage[a4paper,margin=0.5in]{geometry}

% Setup the language.
\usepackage[english]{babel}
\hyphenation{Some-long-word}

% Makes resume-specific commands available.
\usepackage{resume}

\usepackage[T1]{fontenc}

% Enable multi column
\usepackage{multicol}

% To kill the spaces in lists
\usepackage{enumitem}

% No space before multi colk
\setlength\multicolsep{0pt}

%\sloppy  % this to relax whitespacing in favour of straight margins

\begin{document}  % begin the content of the document

% title on top of the document
\begin{center}
\maintitle{Gabriel Ochoa}{}{}
\nobreakvspace{0.3em}  % add some page break averse vertical spacing
\end{center}

% \noindent prevents paragraph's first lines from indenting
% \mbox is used to obfuscate the email address
% \sbull is a spaced bullet
% \href well..
% \\ breaks the line into a new paragraph
\href{mailto:gochoa1@binghamton.edu}{gochoa1@binghamton.edu}\sbull
(914)-483-8190\sbull
\href{https://github.com/gabeochoa}{github.com/gabeochoa}\sbull
\href{https://www.linkedin.com/in/gabemochoa}{linkedin.com/in/gabemochoa}


\roottitle{Experience}

\spacedhrule{0.5em}{0.5em}  % a horizontal line with some vertical spacing before and after

\headedsection  % sets the header for the section and includes any subsections
{\href{http://www.bloomberg.com/company}{Bloomberg L.P.}}
{New York, New York}
{
    \headedsubsection
    {Senior Software Engineer - Network Surveillance Automation}
    {June 2016 - Present}
    {
        \begin{itemize}
            \item Designed/Implemented systems to automate network management and monitoring
            \item Worked alongside Network Design and Operation Engineers on the world's largest private network
            \item Lead Eng. on a persistent key/value store for configuration and state of 150k+ network devices. 
            \item[] Ingests data produced by various network teams contribute data (~60k POSTs / day, > 1TB Total)
            \item[] Used by teams across infrastructure teams through GUI or API (~100k GETs / day)
            \item Implemented system for collecting client-defined metrics to verify state of deployed devices
            \item Created a django library to integrate our team's apps with Bloomberg SSO and Oauth2.0 Services
            \item Mentored four full-time employees and one intern
            \item Assisted HR in interviewing for college and senior hire positions
        \end{itemize}

    }
}
\headedsection  % sets the header for the section and includes any subsections
{}
{}
{
    \headedsubsection
    {Software Engineering Intern - \href{https://www.bloomberg.com/professional/product/vault/}{Vault}}
    {Summer 2015}
    {
        \begin{itemize}
            \item Designed, Tested and Implemented C++ and Java API for an Accumulo DataBase
            \item Used during ingestion to process/query over a 1 billion cloud stored xml files
        \end{itemize}
    }
}
\roottitle{Education}

\spacedhrule{0.5em}{0.5em}  % a horizontal line with some vertical spacing before and after

\headedsection
{\href{http://www.binghamton.edu/index.php}{Binghamton University, State University of New York}}
{Binghamton, New York} {
    \headedsubsection
    {B.S. Computer Science}
    {Sept 2012 - May 2016}
    {}
}

\nobreakvspace{0.5em}  % add some page break averse vertical spacing

\roottitle{Skills}

\spacedhrule{0.5em}{0.5em}  % a horizontal line with some vertical spacing before and after

\inlineskillsection  % special section that has an inline skiller with a 'hanging' paragraph
{Programming languages:}
{ Python, C++, Java, C, C\#, Bash, Perl }

\inlineskillsection  
{Frameworks:}
{ Django/Flask, Unity, OpenGL}

\inlineskillsection
{Technologies:}
{ MySQL/Postgres/SQLite, Git, SaltStack, Jenkins, Splunk, JIRA, \latex }

\inlineskillsection
{Human Languages:}
{English (Native), Korean(Inter.), Spanish(Elem.), Mandarin Chinese (Beginner)}


\nobreakvspace{0.3em}  % add some page break averse vertical spacing

\roottitle{Personal Projects}

\spacedhrule{0.1em}{0.5em}  % a horizontal line with some vertical spacing before and after

\projects
{{\href{https://github.com/gabeochoa/Cosmos}{Cosmos}}}{}
{
    \begin{itemize}[label={}]
        \setlength\itemsep{.005ex}
        \item{An electronic platform for trading fake commodities contracts. C++, Sockets, GTest.}
    \end{itemize}
}

\projects
{{\href{https://github.com/gabeochoa/sokim}{Deceit}} - $\textbf{Best FOSS Hack}$}{BrickHack Spring 2016}
{
    \begin{itemize}[label={}]
        \setlength\itemsep{.005ex}
        \item{Webapp Card Game based on Dixit (the board game). Built with Python, Flask, and Reddit API.}
    \end{itemize}
}

\headedsubsection
{{\href{https://github.com/alanplotko/RoadTrip}{FriendWagon}} - $\textbf{Best Use of AWS Winner}$ }
{BrickHack Spring 2015}
{
    \begin{itemize}[label={}]
    	\setlength\itemsep{.005ex}
        \item{"Uber for Road Trips". Using NodeJS, Spotify and Twilio API. Hosted on AWS.}
    \end{itemize}
}

\end{document}

















